---
title: "FCC 2016 Survey Analysis"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)

FCC_df <- read.csv("2016-FCC-New-Coders-Survey-Data.csv")
dim(FCC_df)

FCC_df$JobRoleInterest<- str_trim(FCC_df$JobRoleInterest)
DSInt_df <- filter(FCC_df,  JobRoleInterest == "Data Scientist / Data Engineer")
View(DSInt_df)

```




```{r}
table(DSInt_df$AttendedBootcamp)


DSInt_df$AttendedBootcamp <- factor(DSInt_df$AttendedBootcamp, levels = c(1, 0),
                                     labels = c('Yes','No'))

table(DSInt_df$AttendedBootcamp)

```

The majority of respondents have not attended a bootcamp before. Considering the small percentage, it makes no sense to look into the question of how many finished and how many got a job afterwords.




```{r}
sum(is.na(DSInt_df$CityPopulation))
ggplot(DSInt_df, aes(x = CityPopulation)) +
  geom_bar()

DSInt_df$IsSoftwareDev <- factor(DSInt_df$IsSoftwareDev, levels = c(1, 0),
                                     labels = c('Yes','No'))

 summary(DSInt_df$CountryLive)
 summary(DSInt_df$EmploymentField)
 summary(DSInt_df$IsSoftwareDev)
 summary(DSInt_df$EmploymentStatus)

```


The marjority of our proppects live in large cities that are 100 thousand large. And a good chunk of our prospects are from the united states. About 267 of our prospects are employed but looking for work. 137 are unemployed but looking for work.


```{r}
summary(DSInt_df$SchoolDegree)
summary(DSInt_df$Income)
summary(DSInt_df$ExpectedEarning)

table(DSInt_df$Gender)

ggplot(DSInt_df, aes(x = ExpectedEarning)) +
  geom_histogram(fill = "blue")


sum(is.na(DSInt_df$ResourceCodecademy))
sum(is.na(DSInt_df$ResourceBlogs))
sum(is.na(DSInt_df$ResourceBooks))
sum(is.na(DSInt_df$ResourceCodeWars))
sum(is.na(DSInt_df$ResourceCoursera))
sum(is.na(DSInt_df$ResourceDevTips))
sum(is.na(DSInt_df$ResourceEdX))
sum(is.na(DSInt_df$ResourceEggHead))
sum(is.na(DSInt_df$ResourceFCC))
sum(is.na(DSInt_df$ResourceGoogle))
sum(is.na(DSInt_df$ResourceHackerRank))
sum(is.na(DSInt_df$ResourceLynda))
sum(is.na(DSInt_df$ResourceMDN))
sum(is.na(DSInt_df$ResourceOdinProj))
sum(is.na(DSInt_df$ResourceOther))
sum(is.na(DSInt_df$ResourcePluralSight))
sum(is.na(DSInt_df$ResourceReddit))
sum(is.na(DSInt_df$ResourceSkillCrush))
sum(is.na(DSInt_df$ResourceSoloLearn))
sum(is.na(DSInt_df$ResourceStackOverflow))
sum(is.na(DSInt_df$ResourceTreehouse))
sum(is.na(DSInt_df$ResourceUdacity))
sum(is.na(DSInt_df$ResourceUdemy))
sum(is.na(DSInt_df$ResourceW3Schools))
sum(is.na(DSInt_df$ResourceYouTube))
```

 Educational level demonstrates that most folks interested in the field have a bachelors degree or higher. 
With that we can create a basic marketing persona. We'll call him Frank. 

Frank is a 24 year old man living in New York City. He graduated from his university with a CS degree and is currently employed but looking to work as a data scientist. He's hoping to make $90,000 in his next role.

 
 
 
```{r}
## Start of part 2 to be completed.  Subsetting dataset for female demographic and following up with how to market

fem <-  filter(DSInt_df, Gender == "female")
View(fem)

 summary(fem$CountryLive)
 summary(fem$EmploymentField)
 summary(fem$IsSoftwareDev)
 summary(fem$EmploymentStatus)
 summary(fem$SchoolDegree)
 summary(fem$Income)
 summary(fem$ExpectedEarning)
```


